Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-10 Reply_Referee1.tex

\item \textit{``The Monte Carlo should also include conditional heteroskedasticity versions of the used DGPs.''}

  Thank you for suggesting additional DGPs. We have performed new simulations using new DGPs with both mild and severe heteroskedasticity, please see the simulations section in the new draft.

\item \textit{``The proofs need to include more detailed steps. Be explicit about bootstrap parameters (e.g. $\tau^{*}$). Provide a detailed proof for the statement that follows after ``the bootstrap ensures that'' in page 19. What do you mean by the last formula of page 20? Also, it is not clear what equality in distribution in the first display of page 21 means. Where is $V(h,b)$ defined? I was unable to find it. The authors need to make sure that the convergence in distribution proof is valid under conditional heteroskedasticity.''}

Thank you very much for pointing out instances in the proofs that might require checking and clarifications.
 We are sorry this was confusing to read. In the new proofs we have added details to the statement ``the bootstrap ensures that'', previously on page 19.
 Since the proof for theorem 2 changed substantially with the adoption of the Wild Bootstrap scheme
 (which addresses the heteroskedasticity issue, as discussed before) we made substantial changes that hopefully
 will make the proof's steps clearer to the reader, addressing the remaining comments.

### 2016-08-10 Reply_Referee2.tex

\item \textit{``In Algorithm 1, use $\Delta(h,b)$ or $\hat{\Delta}(h,b)$ instead of $\Delta^{*}(h,b)$, as there is no bootstrap uncertainty in the estimated bias. Accordingly in Algorithm 2, use $\Delta^{*}(h,b)$ or $\hat{\Delta}^{*}(h,b)$ instead of $\Delta^{**}(h,b)$.''}

\item \textit{``In Algorithm 2.1, it should be ``$\hat{g}_{-}$ and $\hat{g}_{+}$''.''}

 Thanks. It has been corrected.

\item \textit{``Instead of $\hat{\tau}'(h,b)$ and $V'(h,b)$, I recommend using $\hat{\tau}^{bc}(h,b)$ and $V^{bc}(h,b)$ to make the notation more explicit.''}
Thanks for suggesting a notation choice that could make the exposition easier for readers familiar with the literature.  We changed it on the latest draft.

### 2016-08-10 main_paper.tex
Minor language changes to section 5.

The two robust procedures are again very similar to each other and give slightly
larger point estimates in both panels. In Panel A, the ATE increases from 0.030
to 0.055 (CCT and bootstrap). In Panel B, the ATE increases from 0.037
to 0.051 (CCT) and 0.052 (bootstrap). The confidence intervals tend to shift up
as well.  In contrast to the striking differences between the conventional
estimates bias-corrected procedures for the mortality estimates, the differences
in Table~\ref{tbl:3} are much smaller.

>>>>

The two robust procedures are again very similar to each other and give slightly
larger point estimates in both panels. In Panel A, the ATE increases from 0.030
to 0.055 (CCT and bootstrap). In Panel B, the ATE increases from 0.037
to 0.051 (CCT) and 0.052 (bootstrap). The confidence intervals tend to shift up
as well.  In contrast to the striking differences between the conventional
and bias-corrected procedures for the mortality estimates, the differences
in Table~\ref{tbl:3} are much smaller.
